
---
title: "All 'Documented' User Activity inside Content Areas: Skillshub site"
author: "Emma Rand"
output:
  pdf_document: bookdown::pdf_document2
  html_document: bookdown::html_document2
  word_document: default
figsintext: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE,
                      fig.show = "asis")
```

```{r pkg}

library(readxl)
library(janitor)
library(tidyverse)
library(flextable)
```


# User Activity in content areas

Data derived from the "All User Activity inside Content Areas" report from BB for the Skillshub site.
The data were downloaded on 05-08-19 and cover period 01-09-18 to 05-08-19. It comprises the number of hits.


Student record data were downloaded from SES on 05-08-19. This data file includes all students registered in the Biology Department but excludes students recently graduated.

```{r import}
# read in list of all students
# downloaded from biology department on 08-08-19

students <- read_excel("../data/students.xlsx") %>% 
  clean_names()

# read in list of VLE use
# download from VLE 05-08-19 and covered period 01-09-18 to 05-08-19
file <-  "../data/All User Activity inside Content Areas_MG.xlsx"
content_area_summary <- read_excel(file, 
                              sheet = "Content" ) %>% 
  clean_names()

# read in list of excludes
exclude <- read.table("../data/exclude_users.txt",
                      header = TRUE,
                      stringsAsFactors = FALSE)
```

The number of Student records: `r nrow(students)`. 
The number of Registered site users: `r nrow(content_area_summary)`.

Some users involved in the project were excluded. These were: `r exclude$username`
```{r}
# exclude the usernames in exclude from all content_area_summary
content_area_summary <- content_area_summary %>% subset(!(username %in% exclude$username))

# exclude the usernames in exclude from all students
students <- students %>% subset(!(username %in% exclude$username))
```
This left `r nrow(students)` student records and `r nrow(content_area_summary)` registered site users

## Summary for with-record Student users

```{r}
# merge dataframes keeping all rows in content_area_summary
# some student data will be missing for vle users since they have been removed
# but should be possible to get their information - has been requested from the
# office
# students in the list of documented students that were not in the list of registered user
# will not be include

content_area_summary_user <-  content_area_summary %>% 
  merge(students, by = "username", 
        all.x = TRUE) 
```

The student data was combined with the Overall Summary data. 

```{r}
# Get list of usernames for people in VLE but not in student list 
# these are students who graduated or staff
undoc_user <- content_area_summary_user %>% 
  filter(is.na(student_code)) %>% 
  select(name, username)
write.table(undoc_user, 
            file = "../data/recordless2.txt", 
            row.names = FALSE)
```
"Recordless" users, i.e., those without student records were dropped for this analysis. This included students who graduated or staff. These `r nrow(undoc_user) ` recordless users are [here](../data/recordless.txt)

```{r}
# work with the documented users
# these are students in years 2, 3 and 4, (1, 2, 3 as was in 2018-19 academic year)
content_area_summary_doc_user <- content_area_summary_user %>% 
  filter(!username %in% undoc_user$username)
```
This leaves `r nrow(content_area_summary_doc_user) ` site-registered users with records.


### Content hits by Intended award

```{r}
###########################################
# content use by intended award all user
###########################################

content_use_all <- content_area_summary_doc_user %>% 
  group_by(intended_award) %>% 
  summarize(Total = sum(total),
            AcadIinteg = sum(academic_integrity_and_ethics),
            Ackn = sum(acknowledgments),
            Bioinf = sum(bioinformatics),
            Links = sum(biology_webpages_and_other_useful_links),
            Careers = sum(careers),
            ChemHub = sum(chemistry_hub),
            CommSkills = sum(communication_skills),
            DataSkils = sum(data_skills_and_numeracy),
            Feedback = sum(give_us_your_feedback),
            GroupWork = sum(group_work),
            IndepLearn = sum(independent_learning),
            Library = sum(library_resources),
            PracSkills = sum(practical_skills_and_safety),
            Welcome = sum(welcome_page))
```            


```{r award-all}
keys <- names(content_use_all)[-1]
content_use_all %>% flextable() %>% 
  fontsize(size = 10, part = "all") %>% 
  colformat_num(col_keys = keys, 
                digits = 0) %>%
  add_header_lines("Total Content Area hits by award") 
```




### Content hits by Tier 4 status

```{r}
content_use_all <- content_area_summary_doc_user %>%
  group_by(tier4) %>%
  summarize(Total = sum(total),
            AcadIinteg = sum(academic_integrity_and_ethics),
            Ackn = sum(acknowledgments),
            Bioinf = sum(bioinformatics),
            Links = sum(biology_webpages_and_other_useful_links),
            Careers = sum(careers),
            ChemHub = sum(chemistry_hub),
            CommSkills = sum(communication_skills),
            DataSkils = sum(data_skills_and_numeracy),
            Feedback = sum(give_us_your_feedback),
            GroupWork = sum(group_work),
            IndepLearn = sum(independent_learning),
            Library = sum(library_resources),
            PracSkills = sum(practical_skills_and_safety),
            Welcome = sum(welcome_page))
```

```{r tier4-all}
content_use_all %>% flextable() %>% 
  colformat_num(col_keys = keys, 
                digits = 0) %>% 
  fontsize(size = 10, part = "all") %>% 
  add_header_lines("Total content hits by tier 4 status") 
```

