
---
title: "Overall summary of 'Documented' User Activity: Skillshub site"
author: "Emma Rand"
output:
  html_document: bookdown::html_document2
  pdf_document: bookdown::pdf_document2
  word_document: default
figsintext: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE,
                      fig.show = "asis")
```

```{r pkg}

library(readxl)
library(janitor)
library(tidyverse)
library(flextable)
```


# Overall summary of User Activity

Summary data derived from the "Overall Summary of User Activity" report from BB for the Skillshub site.
The data were downloaded on 05-08-19 and cover period 01-09-18 to 05-08-19. It comprises the number of hits per user on BB "Access or Application" elements (full list [here](info/BB_Area_ID.txt)). There were only two elements with hits, "Content" and "Journal". It includes all users registered on the site - students and staff.


Student record data were downloaded from SES on 05-08-19. This data file includes all students registered in the Biology Department but excludes students recently graduated.

```{r import}
# read in list of all students
# downloaded from biology department on 08-08-19

students <- read_excel("../data/students.xlsx") %>% 
  clean_names()

# read in list of VLE use
# download from VLE 05-08-19 and covered period 01-09-18 to 05-08-19
file <-  "../data/Overall Summary of User Activity_MG.xlsx"
overall_summary <- read_excel(file, 
                              sheet = "Activity" ) %>% 
  clean_names()

# read in list of excludes
exclude <- read.table("../data/exclude_users.txt",
                      header = TRUE,
                      stringsAsFactors = FALSE)
```

The number of Student records: `r nrow(students)`. 
The number of Registered site users: `r nrow(overall_summary)`.

Some users involved in the project were excluded. These were: `r exclude$username`
```{r}
# exclude the usernames in exclude from all overall_summary
overall_summary <- overall_summary %>% subset(!(username %in% exclude$username))

# exclude the usernames in exclude from all students
students <- students %>% subset(!(username %in% exclude$username))
```
This left `r nrow(students)` student records and `r nrow(overall_summary)` registered site users

## Summary for with-record Student users

```{r}
# merge dataframes keeping all rows in overall_summary
# some student data will be missing for vle users since they have been removed
# but should be possible to get their information - has been requested from the
# office
# students in the list of documented students that were not in the list of registered user
# will not be include

overall_summary_user <-  overall_summary %>% 
  merge(students, by = "username", 
        all.x = TRUE) 
```

The student data was combined with the Overall Summary data. 

```{r}
# Get list of usernames for people in VLE but not in student list 
# these are students who graduated or staff
undoc_user <- overall_summary_user %>% 
  filter(is.na(student_code)) %>% 
  select(name, username)
write.table(undoc_user, 
            file = "../data/recordless.txt", 
            row.names = FALSE)
```
"Recordless" users, i.e., those without student records were dropped for this analysis. This included students who graduated or staff. These `r nrow(undoc_user) ` recordless users are [here](../data/recordless.txt)

```{r}
# work with the documented users
# these are students in years 2, 3 and 4, (1, 2, 3 as was in 2018-19 academic year)
overall_summary_doc_user <- overall_summary_user %>% 
  filter(!username %in% undoc_user$username)
```
This leaves `r nrow(overall_summary_doc_user) ` site-registered users with records.


### Content hits by Intended award
#### Summary for all site-registered users
Includes those registered who made no use
```{r}
###########################################
# content use by intended award all user
###########################################

content_use_all <- overall_summary_doc_user %>% 
  group_by(intended_award, .drop = FALSE) %>% 
  summarize(n = length(content),
            mean = mean(content),
            sd = sd(content),
            median = median(content),
            max = max(content),
            min = min(content))
```            


```{r award-all}
content_use_all %>% flextable() %>% 
  colformat_num(col_keys = c("mean", "sd"), 
                digits = 2) %>% 
  colformat_num(col_keys = c("median", "max", "min"), 
                digits = 0) %>% 
  fontsize(size = 10, part = "all") %>% 
  add_header_lines("Summary content hits for all site-registered users") 
```




#### Summary for active site-registered users
Only those that had at least one hit
```{r}
content_use_active <- overall_summary_doc_user %>% 
  filter(content > 0) %>% 
  group_by(intended_award, .drop = FALSE) %>% 
  summarize(n = length(content),
            mean = mean(content),
            sd = sd(content),
            median = median(content),
            max = max(content),
            min = min(content))
```

```{r award-active}
content_use_active %>% flextable() %>% 
  colformat_num(col_keys = c("mean", "sd"), 
                digits = 2) %>% 
  colformat_num(col_keys = c("median", "max", "min"), 
                digits = 0) %>% 
  fontsize(size = 10, part = "all") %>% 
  add_header_lines("Summary content hits for the site-registered users with at least one hit") 
```


#### Summary for inactive site-registered users
Who are the site-registerd no users
```{r}
content_use_nonuser <- overall_summary_doc_user %>% 
  filter(content == 0) %>% 
  group_by(intended_award) %>% 
  summarize(n = length(content))
```

```{r award-inactive}
content_use_nonuser %>% flextable() %>% 
  fontsize(size = 10, part = "all") %>% 
  add_header_lines("Distribution on non-users") 
```



#### Percent use by Intended award
```{r}
content_use_all <- content_use_nonuser %>% 
  select(n, intended_award) %>% 
  merge(content_use_all, by = "intended_award")

content_use_all$percentuse <- 100 * (content_use_all$n.y - content_use_all$n.x) / content_use_all$n.y

```

```{r award-active-pcent}
content_use_all %>% 
  select(intended_award, percentuse) %>% 
  flextable() %>% 
  fontsize(size = 10, part = "all")%>% 
  colformat_num(col_keys = c("percentuse"), 
                digits = 2) %>% 
  add_header_lines("Percentage use per Intended award") 
```


### Content hits by block
#### Summary for UG site-registered users
UG only, excludes taught and research masters and phd.
Includes those registered who made no use
```{r}
ug <- c("MBIOL Master of Biology", "MBIOMEDSCI Master of Biomedical Science", "BSC Bachelor of Science", "MBIOCHEM Master of Biochemistry")
overall_summary_doc_user_ug <- overall_summary_doc_user %>% 
  filter(intended_award %in% ug)
```

This is `r nrow(overall_summary_doc_user_ug)` documented users


```{r}
###########################################
# content use by block ug user
###########################################

content_use_all <- overall_summary_doc_user_ug %>% 
  group_by(block, .drop = FALSE) %>% 
  summarize(n = length(content),
            mean = mean(content),
            sd = sd(content),
            median = median(content),
            max = max(content),
            min = min(content))
```            


```{r block-all}
content_use_all %>% flextable() %>% 
  colformat_num(col_keys = c("mean", "sd"), 
                digits = 2) %>% 
  colformat_num(col_keys = c("median", "max", "min"), 
                digits = 0) %>% 
  fontsize(size = 10, part = "all") %>% 
  add_header_lines("Summary content hits for all site-registered UG users") 
```




#### Summary for active site-registered UG users
Only those that had at least one hit
```{r}
content_use_active <- overall_summary_doc_user_ug %>% 
  filter(content > 0) %>% 
  group_by(block, .drop = FALSE) %>% 
  summarize(n = length(content),
            mean = mean(content),
            sd = sd(content),
            median = median(content),
            max = max(content),
            min = min(content))
```

```{r block-active}
content_use_active %>% flextable() %>% 
  colformat_num(col_keys = c("mean", "sd"), 
                digits = 2) %>% 
  colformat_num(col_keys = c("median", "max", "min"), 
                digits = 0) %>% 
  fontsize(size = 10, part = "all") %>% 
  add_header_lines("Summary content hits for the site-registered UG users with at least one hit") 
```


#### Summary for inactive site-registered UG users
Who are the site-registerd no users
```{r}
content_use_nonuser <- overall_summary_doc_user_ug %>% 
  filter(content == 0) %>% 
  group_by(block) %>% 
  summarize(n = length(content))
```

```{r block-inactive}
content_use_nonuser %>% flextable() %>% 
  fontsize(size = 10, part = "all") %>% 
  add_header_lines("Distribution on non-users") 
```


#### Percent use by Bloc
```{r}
content_use_all <- content_use_nonuser %>% 
  select(n, block) %>% 
  merge(content_use_all, by = "block")

content_use_all$percentuse <- 100 * (content_use_all$n.y - content_use_all$n.x) / content_use_all$n.y

```

```{r block-active-pcent}
content_use_all %>% 
  select(block, percentuse) %>% 
  flextable() %>% 
  fontsize(size = 10, part = "all")%>% 
  colformat_num(col_keys = c("percentuse"), 
                digits = 2) %>% 
  add_header_lines("Percentage use per Block") 
```


### Content hits by Tier 4 status
#### Summary for all site-registered users
Includes those registered who made no use
```{r}
content_use_all <- overall_summary_doc_user %>%
  group_by(tier4) %>%
  summarize(n = length(content),
            mean = mean(content),
            sd = sd(content),
            median = median(content),
            max = max(content),
            min = min(content))
```

```{r tier4-all}
content_use_all %>% flextable() %>% 
  colformat_num(col_keys = c("mean", "sd"), 
                digits = 2) %>% 
  colformat_num(col_keys = c("median", "max", "min"), 
                digits = 0) %>% 
  fontsize(size = 10, part = "all") %>% 
  add_header_lines("Summary content hits for all site-registered users") 
```

#### Summary for active site-registered users
Only those that had at least one hit
```{r}
content_use_active <- overall_summary_doc_user %>%
  filter(content > 0) %>%
  group_by(tier4) %>%
  summarize(n = length(content),
            mean = mean(content),
            sd = sd(content),
            median = median(content),
            max = max(content),
            min = min(content))
```

```{r tier4-active}
content_use_active %>% flextable() %>% 
  colformat_num(col_keys = c("mean", "sd"), 
                digits = 2) %>% 
  colformat_num(col_keys = c("median", "max", "min"), 
                digits = 0) %>% 
  fontsize(size = 10, part = "all") %>% 
  add_header_lines("Summary content hits for the site-registered users with at least one hit") 
```

#### Summary for inactive site-registered users
Who are the site-registerd no users
```{r}
content_use_nonuser <- overall_summary_doc_user %>% 
  filter(content == 0) %>% 
  group_by(tier4) %>% 
  summarize(n = length(content))
```

```{r tier4-inactive}
content_use_nonuser %>% flextable() %>% 
  fontsize(size = 10, part = "all") %>% 
  add_header_lines("Distribution on non-users") 
```


#### Percent use by Tier 4
```{r}
content_use_all <- content_use_nonuser %>% 
  select(n, tier4) %>% 
  merge(content_use_all, by = "tier4")

content_use_all$percentuse <- 100 * (content_use_all$n.y - content_use_all$n.x) / content_use_all$n.y

```

```{r tier4-active-pcent}
content_use_all %>% 
  select(tier4, percentuse) %>% 
  flextable() %>% 
  fontsize(size = 10, part = "all")%>% 
  colformat_num(col_keys = c("percentuse"), 
                digits = 1) %>% 
  add_header_lines("Percentage use per Intended award") 
```


### Content hits by Intended award and Tier 4 status

#### Summary for active site-registered users
Only those that had at least one hit
```{r}
content_use_activeN <- overall_summary_doc_user %>%
  filter(content > 0) %>%
  filter(tier4 == "N") %>% 
  group_by(intended_award, .drop = FALSE) %>%
  summarize(N = length(content))

content_use_activeY <- overall_summary_doc_user %>%
  filter(content > 0) %>%
  filter(tier4 == "Y") %>% 
  group_by(intended_award, .drop = FALSE) %>%
  summarize(N = length(content))

content_use_active <- content_use_activeN %>% 
  merge(content_use_activeY, by = "intended_award", all.x = TRUE)



```


```{r tier4-award-active}
content_use_active %>% flextable() %>% 
  set_header_labels(N.x = "N", N.y = "Y" ) %>% 
  add_header_row(values = c("","Tier 4 status"), colwidths = c(1, 2)) %>% 
  align(align = "right", part = "header") %>% 
  fontsize(size = 10, part = "all") %>% 
  add_header_lines("Number of users with at least one hit by award and tier 4 status") 
```

