
---
title: "Overall summary of User Activity: Skillshub site"
author: "Emma Rand"
output:
  html_document: bookdown::html_document2
  pdf_document: bookdown::pdf_document2
  word_document: default
figsintext: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE,
                      fig.show = "asis")
```

```{r pkg}

library(readxl)
library(janitor)
library(tidyverse)
library(flextable)
```


# Overall summary of User Activity

Summary data derived from the "Overall Summary of User Activity" report from BB for the Skillshub site.
The data were downloaded on 05-08-19 and cover period 01-09-18 to 05-08-19. It comprises the number of hits per user on BB "Access or Application" elements (full list [here](info/BB_Area_ID.txt)). There were only two elements with hits, "Content" and "Journal". It includes all users registered on the site - students and staff.


```{r import}
# read in list of VLE use
# download from VLE 05-08-19 and covered period 01-09-18 to 05-08-19
file <-  "../data/Overall Summary of User Activity_MG.xlsx"
overall_summary <- read_excel(file, 
                              sheet = "Activity" ) %>% 
  clean_names()

# read in list of excludes
exclude <- read.table("../data/exclude_users.txt",
                      header = TRUE,
                      stringsAsFactors = FALSE)
```

The number of Registered site users: `r nrow(overall_summary)`.

Some users involved in the project were excluded. These were: `r exclude$username`
```{r}
# exclude the usernames in exclude from all overall_summary
overall_summary <- overall_summary %>% subset(!(username %in% exclude$username))

```
This left `r nrow(overall_summary)` registered site users

## Summary for all users

Includes those who made no use
```{r}
###########################################
# content use by all user
###########################################

content_use_all <- overall_summary %>% 
  summarize(n = length(content),
            mean = mean(content),
            sd = sd(content),
            median = median(content),
            max = max(content),
            min = min(content))
```            


```{r all}
content_use_all %>% flextable() %>% 
  colformat_num(col_keys = c("mean", "sd"), 
                digits = 2) %>% 
  colformat_num(col_keys = c("median", "max", "min"), 
                digits = 0) %>% 
  fontsize(size = 10, part = "all") %>% 
  add_header_lines("Summary content hits for all site-registered users") 
```




#### Summary for active site-registered users
Only those that had at least one hit
```{r}
content_use_active <- overall_summary %>% 
  filter(content > 0) %>% 
  summarize(n = length(content),
            mean = mean(content),
            sd = sd(content),
            median = median(content),
            max = max(content),
            min = min(content))
```

```{r active}
content_use_active %>% flextable() %>% 
  colformat_num(col_keys = c("mean", "sd"), 
                digits = 2) %>% 
  colformat_num(col_keys = c("median", "max", "min"), 
                digits = 0) %>% 
  fontsize(size = 10, part = "all") %>% 
  add_header_lines("Summary content hits for the site-registered users with at least one hit") 
```

